---
title: "SPS-DATA607-ASSIGNMENT-3"
author: "Tage N Singh"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,load-requirements,echo=FALSE,message=TRUE, warning=FALSE}
library(datasets)
library(ggplot2)
library(dplyr)
library("tidyverse")
#library(RMySQL)

```

## Question 1

```{r,Q1}

#cmajors <- read.csv("college-majors.csv")

cmajors <- read.csv("https://raw.githubusercontent.com/tagensingh/SPS-DATA607-ASSIGNMENT-3/main/college-majors.csv")

class(cmajors)

tibble(cmajors)

#_________________________________________________________

#**The Answer to Question 1**

dplyr::filter(cmajors, grepl('DATA|STATISTICS', Major))

#__________________________________________________________

```

## Question 2

```{r,Q2}

### The initial dataset is as follows
(matches <- str_subset(fruit, pattern = "l.*e"))

## manipolating 

frame1 <-list(match = intersect(matches, str_subset(fruit, pattern = "l.+e")))
#no_match = setdiff(matches, str_subset(fruit, pattern = "l.+e")))

frame1


class(frame1)

```

## Question 3 

#### 1. (.)\1\1 - The same character appears three times in a row. E.g. "zzz"

#### 2. "(.)(.)\\2\\1" - This is a  pair of characters followed by the same pair of characters in reversed order. E.g. "noon" or "saas".

#### 3. (..)\1 - This is two characters repeated. E.g. "a1a1" or "U2U2

#### 4. "(.).\\1.\\1" - A character followed by any character, the original character, any other character, the original character again. E.g. "abaca", "z0z0z".

#### 5. "(.)(.)(.).*\\3\\2\\1" - Three characters followed by zero or more characters of any kind followed by the same three characters but in reverse order. E.g. "abctagessinghcba" or "123456321" or "a1a6789a1a"

## Question 4

```{r,Q41}

### Q4-1

#### Words that start and end with the same character, from the "words" dataset

str_subset(words, "^(.)((.*\\1$)|\\1?$)")

```

```{r,Q42}

### Q4-2

#### Pairs of Repeated letters - "london' in this case

str_subset("london", "([A-Za-z][A-Za-z]).*\\1")

#### Pairs of Repeated letters - from the "words" dataset.

str_subset(words, "([A-Za-z][A-Za-z]).*\\1")

```


```{r,Q43}

### Q4-3

#### One letter repeated in at least three places - "nineteen" in this case

str_subset("nineteen", "([a-z]).*\\1.*\\1")

#### One letter repeated in at least three places - from the "words" dataset.

str_subset(words, "([a-z]).*\\1.*\\1")

```
